Holomorphic field theories and higher algebra

### 2024-09-20 draft.tex
switching computers might be a mistake for me

For an example that mixes several types, see Section~\ref{sec: seiberg}
where we discuss a holomorphic analog of quantum chromodynamics (QCD), the theory that governs the strong force and quarks.

@@

\owen{We discussed having the following:
\begin{itemize}
\item Quick overview for topological field theories (=analytic content is de Rham complex): 
\begin{itemize}
\item Axelrod-Singer-Kontsevich method via compactified configuration spaces (Fulton-MacPherson) guarantees no divergences for individual graphs and organizes/clarifies analysis of anomalies
\item Explain what this means in terms of Theorem 3.6 (Elliott-Safronov) and Corollary 4.6 (about existence of functorial field theories)
\item Mention the connection with formality of the $E_d$ operads and related outgrowths in topology 
\end{itemize} 
\item Overview the history of the holomorphic case, with citations
\item Describe a version of Minghao's results (and those of Gaiotto {\it et al}) that emphasizes no divergences for individual graphs and the consequences for anomalies (e.g., relevant wheels for 1-loop and higher loop generalization via Laman graphs)
\item Explain what this means in terms of Theorem 3.9 (existence of polydiscs algebras)
\end{itemize}}

\owen{Old copy that might be recycled into final version}

So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
In the topological setting, renormalization is very well-controlled.
The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.

In other words, by a judicious choice of gauge-fixing, 
we find that the one-loop Feynman diagrams have no UV divergences.
Moreover, no higher loop diagrams appear (for combinatorial reasons),
and the action functional satisfies the quantum master equation.
\brian{this comment does not apply in general, only for cotangent theories.}
See Section~\ref{sec: susytwist revisited} for some further discussion.

Although holomorphic field theories had already appeared in practice,
my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
He did the following:
\begin{itemize}
\item established key analytic results about holomorphic renormalization, 
showing that it is highly manageable, with no counterterms to 1-loop; and
\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
\end{itemize}
These apply to all holomorphic theories on $\CC^n$,
but the techniques typically extend to more general complex manifolds.

\brian{Brian's stuff below}

@@

\subsection{Holomorphic chromodynamics and steps towards holomorphic QCD}

>>>>

For an example that mixes several types and that is a holomorphic analog of quantum chromodynamics (QCD), the theory that governs the strong force and quarks,
see Section~\ref{sec: seiberg}.

@@

@@

\subsection{Holomorphic QCD}
